Learning Discrete-valued Bayesian Networks from Mixed Data

### 2015-11-17 BN_discretizer_paper.tex
pre-Mykel meeting

Bayesian networks \citep{Pearl_1988, PGM_2009} are an increasingly popular method for modeling uncertainty and causality in science and engineering.
They provide an efficient factorization of the joint probability distribution over a set of random variables.
Bayesian networks first emerged from artificial intelligence research and have been applied to a wide variety of problems, ranging from decision-making systems \citep{DMU_2015} \mykel{better to use a primary source} to medical diagnoses \citep{Lustgarten_2011}.
In most cases, we assume that all random variables in Bayesian networks are discrete, since many Bayesian network learning algorithms are unable to deal with continuous variables efficiently.
However, many applications   +Bayesian networks \citep{Pearl_1988, PGM_2009} are an increasingly popular method for modeling uncertainty and causality in science and engineering.
They provide an efficient factorization of the joint probability distribution over a set of random variables.
Bayesian networks first emerged from artificial intelligence research and have been applied to a wide variety of problems, ranging from decision-making systems \citep{DMU_2015} to medical diagnoses \citep{Lustgarten_2011}.
In most cases, we assume that all random variables in Bayesian networks are discrete, since many Bayesian network learning algorithms are unable to deal with continuous variables efficiently.
However, many applications require the use of continuous variables, such as position and velocity in dynamic systems \mykel{cite Kochenderfer JGCD article on encounter modeling}.

There are two common approaches to extending Bayesian networks to continuous variables.
The first is to model the conditional probability density of each continuous variable using specific families of parametric distributions, and then to redesign Bayesian network learning algorithms based on their parameters.
One successful example is belief propagation in Gaussian graphical models \citep{Weiss_2011}.
For other parametric distributions \citep{Ihler_2009} and non-linear functions~\todo{[cite]}, these redesigned algorithms are computationally expensive and do not perform well.
\mykel{$\bigstar$ We need to discuss this; talk about algorithms for inference and structure learning, expectation propagation, Gibbs, BVGS}

@@

This section describes experiments conducted to evaluate the proposed methods.
All experiments were run on datasets from the publically available Irvine machine learning repository \citep{Lichman:2013}.
Variables are labelled alphabetically in the order given on the dataset information webpage.
Subscripts inducate the number of discretized intervals.
Shaded nodes are originally discrete and unshaded nodes are originally continuous.

>>>>

Bayesian networks \citep{Pearl_1988, PGM_2009} are an increasingly popular method for modeling uncertainty and causality in science and engineering.
They provide an efficient factorization of the joint probability distribution over a set of random variables.
Bayesian networks first emerged from artificial intelligence research and have been applied to a wide variety of problems, ranging from decision-making systems \citep{DMU_2015} \mykel{better to use a primary source} to medical diagnoses \citep{Lustgarten_2011}.
In most cases, we assume that all random variables in Bayesian networks are discrete, since many Bayesian network learning algorithms are unable to deal with continuous variables efficiently.
However, many applications   +Bayesian networks \citep{Pearl_1988, PGM_2009} are an increasingly popular method for modeling uncertainty and causality in science and engineering.
They provide an efficient factorization of the joint probability distribution over a set of random variables.
Bayesian networks first emerged from artificial intelligence research and have been applied to a wide variety of problems, ranging from decision-making systems \citep{DMU_2015} to medical diagnoses \citep{Lustgarten_2011}.
\mykel{packages such as ....}
In most cases, we assume that all random variables in Bayesian networks are discrete, since many Bayesian network learning algorithms are unable to deal with continuous variables efficiently.
However, many applications require the use of continuous variables, such as position and velocity in dynamic systems \citep{kochenderfer2010airspace}.

There are two common approaches to extending Bayesian networks to continuous variables.
The first is to model the conditional probability density of each continuous variable using specific families of parametric distributions, and then to redesign Bayesian network learning algorithms based on their parameters.
One successful example is belief propagation in Gaussian graphical models \citep{Weiss_2011}.
For other parametric distributions and non-linear functions \citep{Ihler_2009}, these redesigned algorithms are computationally expensive and do not perform well.
\mykel{$\bigstar$ We need to discuss this; talk about algorithms for inference and structure learning, expectation propagation, Gibbs, BVGS}

@@

This section describes experiments conducted to evaluate the proposed methods.
All experiments were run on datasets from the publically available Irvine machine learning repository \citep{Lichman_2013}.
Variables are labelled alphabetically in the order given on the dataset information webpage.
Subscripts inducate the number of discretized intervals.
Shaded nodes are originally discrete and unshaded nodes are originally continuous.
